### 2023-04-09 chapter2/chapter2.tex
Tweaked wording about normalizing rates to make less awkward
Added scores figure to chapter 2

\section{Results}
\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/substitution.png}
\centering
\caption{\textbf{Amino acid substitution models fit to disorder and order regions.}
\textbf{(A)} Amino acid frequencies of substitution models. Amino acid symbols are ordered by their enrichment in disorder regions, calculated as the disorder-to-order ratio of their frequencies. Error bars represent standard deviations over models fit to different meta-alignments ($n = 25$). \textbf{(B-C)} Exchangeability coefficients of disorder and order regions, respectively, averaged over meta-alignments. \textbf{(D)} $\log_{10}$ disorder-to-order ratios of exchangeability coefficients. \textbf{(E-F)} Rate coefficients of disorder and order regions, respectively, averaged over meta-alignments. The vertical and horizontal axes indicate the initial and target amino acids, respectively. \textbf{(G)} $\log_{10}$ disorder-to-order ratios of rate coefficients.}
\label{fig:substitution}
\end{figure}

@@

\subsection{Fitting amino substitution models}
To fit amino acid substitution matrices to disorder and order regions, 25 meta-alignments were constructed by randomly sampling 100,000 columns from the respective subsets in the filtered regions derived from the 30 residue length cutoff. To determine the effect of gaps, the maximum fraction of gaps was set at 0, 50, 100\%. The combination of the region types and sampling strategy yielded six different sets of meta-alignments. A GTR20 substitution model with four FreeRate categories and optimized state frequencies was fit to each meta-alignment using IQ-TREE 1.6.12~\cite{Nguyen2014}. Exchangeability and rate coefficients were normalized to make the average rate of each model equal to 1. All figures are derived from the maximum 50\% gap fraction meta-alignment set unless otherwise noted.

>>>>

\section{Results}
\begin{figure}[h!]
\includegraphics[width=\textwidth]{scores/out/scores_07E3.png}
\centering
\caption{\textbf{Analyses of disorder scores.}
\textbf{(A)} Example alignment with the disorder scores of its sequences. Higher scores indicate a higher probability of disorder. Disorder score traces are colored by the position of its associated species on the phylogenetic tree. \textbf{(B)} Correlations between disorder scores and feature contrasts in regions. Asterisks indicate statistically significant correlations as computed by permutation tests ($p < 0.001$). \textbf{(C-D)} Example scatter plots showing correlations plotted in panel B. \textbf{(E)} GO term analysis of regions with rapidly evolving disorder scores. Only terms whose $p$-values are below 0.001 are shown.}
\label{fig:scores}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/substitution.png}
\centering
\caption{\textbf{Amino acid substitution models fit to disorder and order regions.}
\textbf{(A)} Amino acid frequencies of substitution models. Amino acid symbols are ordered by their enrichment in disorder regions, calculated as the disorder-to-order ratio of their frequencies. Error bars represent standard deviations over models fit to different meta-alignments ($n = 25$). \textbf{(B-C)} Exchangeability coefficients of disorder and order regions, respectively, averaged over meta-alignments. \textbf{(D)} $\log_{10}$ disorder-to-order ratios of exchangeability coefficients. \textbf{(E-F)} Rate coefficients of disorder and order regions, respectively, averaged over meta-alignments. The vertical and horizontal axes indicate the initial and target amino acids, respectively. \textbf{(G)} $\log_{10}$ disorder-to-order ratios of rate coefficients.}
\label{fig:substitution}
\end{figure}

@@

\subsection{Fitting amino substitution models}
To fit amino acid substitution matrices to disorder and order regions, 25 meta-alignments were constructed by randomly sampling 100,000 columns from the respective subsets in the filtered regions derived from the 30 residue length cutoff. To determine the effect of gaps, the maximum fraction of gaps was set at 0, 50, 100\%. The combination of the region types and sampling strategy yielded six different sets of meta-alignments. A GTR20 substitution model with four FreeRate categories and optimized state frequencies was fit to each meta-alignment using IQ-TREE 1.6.12~\cite{Nguyen2014}. Exchangeability and rate coefficients were normalized, so the average rate of each model was equal to 1. All figures are derived from the maximum 50\% gap fraction meta-alignment set unless otherwise noted.
